---
title: "R Notebook"
output: html_notebook
---

# Libraries

```{r}

library(here)
library(dplyr)
library(tidyverse)
library(sf)
library(data.table)
library(ggplot2)
library(raster)
library(prismatic)
library(arulesCBA)
library(tibble)
library(osmdata)
library(wesanderson)
library(ggpubr)
library(kableExtra)
library(magick)

```


# Observation data
```{r}

filenames <- list.files(here("source"),pattern="*.gpkg$")

layers_s = c("09h30_staying","12h30_staying","15h30_staying","18h30_staying")
layers_m = c("09h30_moving","12h30_moving","15h30_moving","18h30_moving")

list_m = list()
list_s = list()

for (i in filenames) {

filename = i  
  
for (j in layers_s) {
df = st_read(here("source",filename),j)
df$fileid = filename
df$layer = j
df = df %>% dplyr::select(-Photo,-mode,-row,-id)
list_s[[length(list_s)+1]]=df
rm(df)
}

for (j in layers_m) {
df = st_read(here("source",filename),j)
df$fileid = paste0(filename,j)
df$fileid = filename
df$layer = j
df = df %>% dplyr::select(-Direction,-Photo)
list_m[[length(list_m)+1]]=df
rm(df)
}

rm(filename)

}

df_s = rbindlist(list_s,use.names = FALSE) %>% as.data.frame() %>% st_as_sf()
df_s = df_s %>% rename_with(~ gsub(".", "_", .x, fixed = TRUE))
df_s = df_s[!(is.na(df_s$activity)), ]
df_s %>% ggplot() + geom_sf()

df_m = rbindlist(list_m,use.names = FALSE) %>% as.data.frame() %>% st_as_sf()
df_m = df_m %>% rename_with(~ gsub(".", "_", .x, fixed = TRUE))
df_m = df_m[!(is.na(df_m$mouvement)), ]
df_m %>% ggplot() + geom_sf()


```


## IDs
```{r}

#survey_id
df_s$survey_id =
  paste0(
  str_split_i(df_s$fileid,"_",1),"_",
  str_split_i(df_s$fileid,"_",2),"_",
  str_split_i(df_s$fileid,"_",4),"_",
  gsub("h","",str_split_i(df_s$layer,"_",1)),
  "00")

df_m$survey_id =
  paste0(
  str_split_i(df_m$fileid,"_",1),"_",
  str_split_i(df_m$fileid,"_",2),"_",
  str_split_i(df_m$fileid,"_",4),"_",
  gsub("h","",str_split_i(df_m$layer,"_",1)),
  "00")

#observer_id
df_s$observer =
  gsub(".gpkg","",str_split_i(df_s$fileid,"_",5))

df_m$observer =
  gsub(".gpkg","",str_split_i(df_m$fileid,"_",5))

# row_id
df_s$row_id <- paste(df_s$survey_id, ave(df_s$timestamp,df_s$survey_id, FUN = seq_along), sep="_")
df_m$row_id <- paste(df_m$survey_id, ave(df_m$timestamp,df_m$survey_id, FUN = seq_along), sep="_")

#tc
df_s$tc = gsub("h",":",str_split_i(df_s$layer,"_",1))
df_m$tc = gsub("h",":",str_split_i(df_m$layer,"_",1))

```

## Means & totals
```{r}

# Row_total
df_s$row_total = df_s$gender_male+df_s$gender_female

df_s$gender_unknown = 
  ifelse(
    df_s$row_total == 0,
    df_s$age_0_14+df_s$age_15_24+df_s$age_25_44+df_s$age_45_64+df_s$age_65_74+df_s$age_75p,
    df_s$gender_unknown
    )

df_s$row_total = 
  ifelse(
    df_s$row_total == 0,
    df_s$age_0_14+df_s$age_15_24+df_s$age_25_44+df_s$age_45_64+df_s$age_65_74+df_s$age_75p,
    df_s$row_total
    )

df_s = df_s %>% filter(row_total != 0)
df_s = df_s %>% drop_na(activity)
  
df_m$row_total <- df_m$gender_male+df_m$gender_female

df_m$gender_unknown = 
  ifelse(
    df_m$row_total == 0,
    df_m$age_0_14+df_m$age_15_24+df_m$age_25_44+df_m$age_45_64+df_m$age_65_74+df_m$age_75p,
    df_m$gender_unknown
    )

df_m$row_total = 
  ifelse(
    df_m$row_total == 0,
    df_m$age_0_14+df_m$age_15_24+df_m$age_25_44+df_m$age_45_64+df_m$age_65_74+df_m$age_75p,
    df_m$row_total
    )

df_m = df_m %>% filter(row_total != 0)
df_m = df_m %>% drop_na(mouvement)


# Mean age per group
df_s$age_mean <- round(((df_s$age_0_14*7)+(df_s$age_15_24*19.5)+(df_s$age_25_44*34.5)+
                                (df_s$age_45_64*54.5)+(df_s$age_65_74*69.5)+
                                (df_s$age_75p*80))/df_s$row_total,digits = 1)

df_m$age_mean <- round(((df_m$age_0_14*7)+(df_m$age_15_24*19.5)+(df_m$age_25_44*34.5)+
                                (df_m$age_45_64*54.5)+(df_m$age_65_74*69.5)+
                                (df_m$age_75p*80))/df_m$row_total,digits = 1)

```


## Separating columns of time & date from timestamp
```{r}

df_s$date = as.Date(as.POSIXct(as.numeric(df_s$timestamp)/1000, origin="1970-01-01"))
df_m$date = as.Date(as.POSIXct(as.numeric(df_m$timestamp)/1000, origin="1970-01-01"))

df_s$time =
  format(
    as.POSIXct(as.numeric(df_s$timestamp)/1000, origin="1970-01-01", tz = "Europe/Berlin"),
    format = "%H:%M:%S")

df_m$time =
  format(
    as.POSIXct(as.numeric(df_m$timestamp)/1000, origin="1970-01-01", tz = "Europe/Berlin"),
    format = "%H:%M:%S")

```


## Adding coordinates WGS84
```{r}

#conversion of points into spatial feature object 
df_s_lb93 <- st_as_sf(df_s, coords = c("X_lb93", "Y_lb93"), crs = 2154, agr = "constant", remove = FALSE)
  
#conversion of Lambert93 coordinates into pseudo mercator (WGS84, EPSg 3857) for kepler.gl
df_s_wgs84 <- st_transform(df_s_lb93, 4326)
  
#extracting X and Y coordinates from geometry
df_s_xy_wgs84 <- st_coordinates(df_s_wgs84)
  
#replacing longitude and latitude by X and Y respectively
df_s$X_wgs84 <- df_s_xy_wgs84[,1]
df_s$Y_wgs84 <- df_s_xy_wgs84[,2]

```

## Reorder dataframe
```{r}

df_s = df_s[,c(
  "survey_id","row_id",
  "timestamp","date","time","tc",
  "X_lb93","Y_lb93","X_wgs84","Y_wgs84",
  "row_total","gender_male","gender_female","gender_unknown",
  "age_mean","age_0_14", "age_15_24","age_25_44","age_45_64","age_65_74","age_75p",
  "posture","interaction","clothing","exposure","activity","stay_time",
  "observer","layer","fileid","geom")]

df_m = df_m[,c(
  "survey_id","row_id",
  "timestamp","date","time","tc",
  "row_total","gender_male","gender_female","gender_unknown",
  "age_mean","age_0_14", "age_15_24","age_25_44","age_45_64","age_65_74","age_75p",
  "interaction","clothing","exposure","mouvement",
  "observer","layer","fileid","geom")]

```


## clean
```{r}

rm(df_s_lb93)
rm(df_s_wgs84)
rm(df_s_xy_wgs84)
rm(list_s)
rm(list_m)

```


## CRS coordinates and definition
```{r}

df_s_2154 =  df_s
df_m_2154 =  df_m

df_s_4326 =  st_transform(df_s, 4326)
df_m_4326 =  st_transform(df_m, 4326)

# definie the CRS to use in the subsequent scripts
df_s = df_s_4326
df_m = df_m_4326

```


## Export .gpkg files
```{r}

st_write(df_s_2154, 
         dsn=here("outcomes","obs_2154.gpkg"),
         layer='staying',
         append=FALSE,
         layer_options = "OVERWRITE=YES")

st_write(df_s_4326, 
         dsn=here("outcomes","obs_4326.gpkg"),
         layer='staying',
         append=FALSE,
         layer_options = "OVERWRITE=YES")

st_write(df_m_2154, 
         dsn=here("outcomes","obs_2154.gpkg"),
         layer='moving',
         append=FALSE,
         layer_options = "OVERWRITE=YES")

st_write(df_m_4326, 
         dsn=here("outcomes","obs_4326.gpkg"),
         layer='moving',
         append=FALSE,
         layer_options = "OVERWRITE=YES")


```


```{r}



```



# Plots preparation

## context
```{r}

buildings <- read_sf(here("source","geom","context.gpkg"),"buildings")
buildings = st_transform(buildings, 4326)
plot(buildings)

boundary = read_sf(here("source","geom","context.gpkg"),"perimetre") %>% slice(1)
boundary = st_transform(boundary, 4326)
plot(boundary)

zones = read_sf(here("source","geom","context.gpkg"),"zones")
zones = st_transform(zones, 4326)
plot(zones)

track = read_sf(here("source","geom","track.gpkg"),"track3")
track = st_transform(track, 4326)
plot(track)

basemap = stack(here("source","geom","basemap.tif"))
basemap_df = as.data.frame(basemap, xy= TRUE)
basemap_df = 
  basemap_df %>% 
  rename(red = basemap_1, #Rename bands
         green = basemap_2,
         blue = basemap_3) %>%
  filter(red != 0) #drop data w/o rgb information

map = stack(here("source","geom","map_georeferenced_clip.tif"))
map_df = as.data.frame(map, xy= TRUE)
map_df = 
  map_df %>% 
  rename(red = map_georeferenced_clip_1, #Rename bands
         green = map_georeferenced_clip_2,
         blue = map_georeferenced_clip_3) %>%
  filter(red != 0) #drop data w/o rgb information

bbox = st_bbox(st_buffer(boundary,dist = 0, joinStyle="ROUND")) #global

```


## openstreetmaps data
```{r}

# the bounding box, limiting what we fetch
#bbox_osm =
#  data.frame(min = c(bbox["xmin"],bbox["ymin"]),
#             max = c(bbox["xmax"],bbox["ymax"]))
#row.names(bbox_osm) = c("x","y")
#bbox_osm = as.matrix(bbox_osm)  

bbox_osm = 
  getbb(
    place_name = "Nantes",
    featuretype = "city"
    )

# tree
map_tree <- bbox_osm %>% 
  opq() %>% 
  add_osm_feature(key = "natural", 
                  value = "tree") %>% 
  osmdata_sf()

# jardins
map_garden <- bbox_osm %>% 
  opq() %>% 
  add_osm_feature(key = "leisure", 
                  value = c("garden","park")) %>% 
  osmdata_sf()

# jardins
map_grass <- bbox_osm %>% 
  opq() %>% 
  add_osm_feature(key = "landuse", 
                  value = "grass") %>% 
  osmdata_sf()

# fontaines
map_eau <- bbox_osm %>% 
  opq() %>% 
  add_osm_feature(key = "natural", 
                  value = "water") %>% 
  osmdata_sf()

#tramway
map_tram <- bbox_osm %>% 
  opq() %>% 
  add_osm_feature(key = "electrified", 
                  value = "contact_line") %>% 
  osmdata_sf()

#platform
map_tram_platform <- bbox_osm %>% 
  opq() %>% 
  add_osm_feature(key = "public_transport", 
                  value = "platform") %>% 
  osmdata_sf()

#building civic
map_building_civic <- bbox_osm %>% 
  opq() %>% 
  add_osm_feature(key = "building", 
                  value = "civic") %>% 
  osmdata_sf()

bbox_4326 = st_bbox(st_transform(st_as_sfc(bbox), 4326))


ggplot() +
  geom_sf(data = map_garden$osm_polygons, fill = "#9DBF9E", col = "#9DBF9E") +
  geom_sf(data = map_grass$osm_polygons, fill = "#9DBF9E", col = "#9DBF9E") +
  geom_sf(data = map_tram$osm_lines, lwd = 1, colour = "gray") +
  geom_sf(data = map_tram_platform$osm_polygons, col = "gray") +
  geom_sf(data = map_tree$osm_points, size = 0.5, col = "#4A6C6F") +
  geom_sf(data = map_eau$osm_polygons, fill = "#9DDBFF", col = "#9DDBFF") +
  geom_sf(data = st_transform(buildings, 4326), col = "black", fill = "black") +
  geom_sf(data = map_building_civic$osm_polygons, col = "black", fill = "black") +
  xlim(bbox_4326[["xmin"]],bbox_4326[["xmax"]])+
  ylim(bbox_4326[["ymin"]],bbox_4326[["ymax"]])+
  theme_bw()
  
  
```


## theme
```{r}

theme_carto <-
  theme_bw() +
  theme(
    #axis.line=element_blank(),
    axis.text.x=element_blank(),
    axis.text.y=element_blank(),
    axis.ticks=element_blank(),
    axis.title.x=element_blank(),
    axis.title.y=element_blank(),
    #legend.position="none",
    panel.background=element_blank(),
    #panel.border=element_blank(),
    panel.grid.major=element_blank(),
    panel.grid.minor=element_blank(),
    plot.background=element_blank(),
    strip.background=element_rect(fill="black"),
    strip.text = element_text(colour = 'white')
    )

```


## background layer
```{r}
bck =
  ggplot() +
    geom_sf(data = map_garden$osm_polygons, fill = "#9DBF9E", col = "#9DBF9E") +
    geom_sf(data = map_grass$osm_polygons, fill = "#9DBF9E", col = "#9DBF9E") +
    geom_sf(data = map_tram$osm_lines, lwd = 1, col = "grey70") +
    geom_sf(data = map_tram_platform$osm_polygons, col = "grey70") +
    geom_sf(data = map_tree$osm_points, size = 0.5, col = "#4A6C6F") +
    geom_sf(data = map_eau$osm_polygons, fill = "#9DDBFF", col = "#9DDBFF")

bck_atlas =
  ggplot() +
    geom_sf(data = map_garden$osm_polygons, fill = "grey70", col = "grey70") +
    geom_sf(data = map_grass$osm_polygons, fill = "grey70", col = "grey70") +
    geom_sf(data = map_tram$osm_lines, lwd = 1, col = "grey80") +
    geom_sf(data = map_tram_platform$osm_polygons, col = "grey80") +
    geom_sf(data = map_tree$osm_points, size = 0.2, col = "grey30") +
    geom_sf(data = map_eau$osm_polygons, fill = "grey50", col = "grey50")
  
#  geom_raster(
#    data = basemap_df, aes(x = x, y =y), fill = rgb(r = basemap_df$red, g = basemap_df$green, b = basemap_df$blue, maxColorValue = 255),
#    show.legend = FALSE)+
#  geom_raster(
#    data = map_df, aes(x = x, y =y), fill = rgb(r = map_df$red, g = map_df$green, b = map_df$blue, maxColorValue = 255),
#    show.legend = FALSE)
```


## dataframes naming
```{r}

m = df_m
z = zones
#m = st_intersection(m,z)
s = df_s
#s = st_intersection(s,z)

```


# Statistique

## Resume
```{r}

bcs_sum_s =
df_s %>%
  mutate(
    time = as.POSIXct(time,format="%H:%M:%S", tz="Europe/Paris")
  ) %>%
  group_by(survey_id) %>%
  summarise(
    date = first(date),
    heure = first(tc),
    #start = first(time),
    #end = last(time),
    duration = as.numeric(last(time)-first(time)),
    observers = n_distinct(observer),
    observations = n(),
    nbp = sum(row_total),
    age_mean = mean(age_mean),
    gender_female = sum(gender_female)/nbp,
    gender_male = sum(gender_male)/nbp
    ) %>%
  mutate_if(is.numeric, round, digits=1) %>%
  mutate(
    tair_mf = c(24.9,29.3,29.7,25.0, #14/6/2023
                20.0,25.9,25.2,21.8, #15/6/2023
                27.2,30.2,31.7,30.6, #24/6/2023
                21.4,25.3,26.9,25.5, #10/7/2023
                25.2,28.0,26.3,22.1, #18/7/2023
                24.3,28.9,29.9,27.2, #21/8/2023
                24.0,28.5,31.0,28.6, #22/8/2023
                22.7,30.6,34.6,31.7 #23/8/2023
                )
  ) %>%
  #dplyr::select(-survey_id) %>%
  st_drop_geometry()


bcs_sum_m =
df_m %>%
  mutate(
    time = as.POSIXct(time,format="%H:%M:%S", tz="Europe/Paris")
  ) %>%
  group_by(survey_id) %>%
  summarise(
    date = first(date),
    heure = first(tc),
    #start = first(time),
    #end = last(time),
    duration = as.numeric(last(time)-first(time)),
    observers = n_distinct(observer),
    observations = n(),
    nbp = sum(row_total),
    age_mean = mean(age_mean),
    gender_female = sum(gender_female)/nbp,
    gender_male = sum(gender_male)/nbp
    ) %>%
  mutate_if(is.numeric, round, digits=1) %>%
  mutate(
    tair_mf = c(24.9,29.3,29.7,25.0, #14/6/2023
                20.0,25.9,25.2,21.8, #15/6/2023
                27.2,30.2,31.7,30.6, #24/6/2023
                21.4,25.3,26.9,25.5, #10/7/2023
                25.2,28.0,26.3,22.1, #18/7/2023
                24.3,28.9,29.9,27.2, #21/8/2023
                24.0,28.5,31.0,28.6, #22/8/2023
                22.7,30.6,34.6,31.7 #23/8/2023
                )
  ) %>%
  #dplyr::select(-survey_id) %>%
  st_drop_geometry()


bcs_sum_s %>%
  group_by(date) %>%
  summarise(
    jour = weekdays(first(date), abbreviate = T),
    tair_mf_m = mean(tair_mf),
    campagnes_n = n_distinct(survey_id),
    enqueteurs_n = mean(observers),    
    duree_m = mean(duration),
    observations_m = mean(observations),
    personnes_m = mean(nbp),
    age_m = mean(age_mean),
    hommes_p = mean(gender_male),
    femmes_p = mean(gender_female)
  ) %>%
  mutate_at(vars(campagnes_n,enqueteurs_n,observations_m,personnes_m), round, digits=0) %>%
  mutate_at(vars(tair_mf_m,duree_m,age_m), round, digits=1) %>%
  mutate_at(vars(hommes_p,femmes_p), round, digits=2) %>%
  kable(
    format = "html",
    col.names = c("Date","Jour","Tair MF (°C)","Campagnes","Enqueteurs","Durée (min.)","Observations","Personnes","Age","Hommes (%)","Femmes (%)"),
    align=rep('lcccccccccc'),
    caption = "Situations statiques, résumé par journée.") %>%
  kable_styling(bootstrap_options = c("striped","hover","bordered"), full_width = F, html_font = "Times New Roman") %>%
  column_spec(1, width = "7em", bold = T) %>%
  as_image(file = here("outcomes","obs_resume_jour_s.jpg"), zoom = 3)


bcs_sum_m %>%
  group_by(date) %>%
  summarise(
    jour = weekdays(first(date), abbreviate = T),
    tair_mf_m = mean(tair_mf),
    campagnes_n = n_distinct(survey_id),
    enqueteurs_n = mean(observers),    
    duree_m = mean(duration),
    observations_m = mean(observations),
    personnes_m = mean(nbp),
    age_m = mean(age_mean),
    hommes_p = mean(gender_male),
    femmes_p = mean(gender_female)
  ) %>%
  mutate_at(vars(campagnes_n,enqueteurs_n,observations_m,personnes_m), round, digits=0) %>%
  mutate_at(vars(tair_mf_m,duree_m,age_m), round, digits=1) %>%
  mutate_at(vars(hommes_p,femmes_p), round, digits=2) %>%
  kable(
    format = "html",
    col.names = c("Date","Jour","Tair MF (°C)","Campagnes","Enqueteurs","Durée (min.)","Observations","Personnes","Age","Hommes (%)","Femmes (%)"),
    align=rep('lcccccccccc'),
    caption = "Situations en mouvement, résumé par journée.") %>%
  kable_styling(bootstrap_options = c("striped","hover","bordered"), full_width = F, html_font = "Times New Roman") %>%
  column_spec(1, width = "7em", bold = T) %>%
  as_image(file = here("outcomes","obs_resume_jour_m.jpg"), zoom = 3)



```


## frequentation
```{r}

plot_s =
df_s %>%
  group_by(survey_id) %>%
  summarise(
    date = as.character(first(date)),
    time = first(tc),
    ref = paste0(date," ",time),
    nbp = sum(row_total)
  ) %>%
  dplyr::select(-survey_id) %>%
  st_drop_geometry() %>%
  ggplot(aes(x = ref, y = nbp, fill = date)) +
    geom_col() +
    scale_fill_manual(values = wes_palette("Royal1", 8, type = "continuous")) +
  ylim(0,170)+
  labs(
    title = "Situations statiques",
    x = "",
    y = "frequentation (nb personnes)"
  ) +
  theme_linedraw() +
  theme(
    axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
    legend.position = "none")


plot_m =
df_m %>%
  group_by(survey_id) %>%
  summarise(
    date = as.character(first(date)),
    time = first(tc),
    ref = paste0(date," ",time),
    nbp = sum(row_total)
  ) %>%
  dplyr::select(-survey_id) %>%
  st_drop_geometry() %>%
  ggplot(aes(x = ref, y = nbp, fill = date)) +
    geom_col() +
    scale_fill_manual(values = wes_palette("Royal1", 8, type = "continuous")) +
  ylim(0,170)+
  labs(
    title = "Situations en mouvement",
    x = "",
    y = ""
  ) +
  theme_linedraw() +
  theme(
    axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
    legend.position = "none")

ggarrange(plot_s,plot_m)

ggsave(here("outcomes","obs_general_frequentation.jpg"), width = 3000, height = 1500, units = "px", dpi = 200)

```


```{r}

df_s %>%
  group_by(survey_id,stay_time) %>%
  summarise(
    date = as.character(first(date)),
    time = first(tc),
    ref = paste0(date," ",time),
    nbp = sum(row_total)
  ) %>%
  st_drop_geometry() %>%
  dplyr::select(-survey_id) %>%
  drop_na(stay_time) %>%
  ggplot(aes(x = ref, y = nbp, fill = stay_time)) +
    geom_col() +
    scale_fill_manual(values = wes_palette("Royal1", 8, type = "continuous"),
                      limits = c("0_2min_short","3_6min_brief","7_12min_break","13_20min_long")) +
  ylim(0,170) +
  labs(
    title = "Situations statiques. Temps de séjour",
    x = "",
    y = ""
  ) +
  theme_linedraw() +
  theme(
    axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

ggsave(here("outcomes","obs_stat_s_temps.jpg"), width = 2000, height = 1500, units = "px", dpi = 200)



df_s %>%
  group_by(survey_id,activity) %>%
  summarise(
    date = as.character(first(date)),
    time = first(tc),
    ref = paste0(date," ",time),
    nbp = sum(row_total)
  ) %>%
  st_drop_geometry() %>%
  dplyr::select(-survey_id) %>%
  drop_na(activity) %>%
  ggplot(aes(x = ref, y = nbp, fill = activity)) +
    geom_col() +
    scale_fill_manual(values = wes_palette("Royal1", 20, type = "continuous")) +
  ylim(0,170) +
  labs(
    title = "Situations statiques. Activité",
    x = "",
    y = ""
  ) +
  theme_linedraw() +
  theme(
    axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

ggsave(here("outcomes","obs_stat_s_activite.jpg"), width = 2000, height = 1500, units = "px", dpi = 200)

df_s %>%
  group_by(survey_id,posture) %>%
  summarise(
    date = as.character(first(date)),
    time = first(tc),
    ref = paste0(date," ",time),
    nbp = sum(row_total)
  ) %>%
  st_drop_geometry() %>%
  dplyr::select(-survey_id) %>%
  drop_na(posture) %>%
  ggplot(aes(x = ref, y = nbp, fill = posture)) +
    geom_col() +
    scale_fill_manual(values = wes_palette("Royal1", 8, type = "continuous")) +
  ylim(0,170) +
  labs(
    title = "Situations statiques. Posture",
    x = "",
    y = ""
  ) +
  theme_linedraw() +
  theme(
    axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

ggsave(here("outcomes","obs_stat_s_posture.jpg"), width = 2000, height = 1500, units = "px", dpi = 200)

```


# Plots

## Single observations
```{r}
bck +
#ggplot()+
  geom_sf(data = m, lwd = 0.4, col = "black", alpha = 0.1)+
  scale_fill_manual(values = wes_palette("Zissou1", 2, type = "discrete")) +
  geom_sf(data = s, alpha = 0.5, col = "black", shape = 3, aes(size = row_total/2))+
  geom_sf(data = map_tree$osm_points, size = 1, col = "#4A6C6F") +
  geom_sf(data = map_building_civic$osm_polygons, col = "grey25", fill = "grey25") +
  geom_sf(data = st_transform(buildings, 4326), col = "grey25", fill = "grey25")+
  xlim(bbox_4326[["xmin"]]+0.0008,bbox_4326[["xmax"]]-0.0003)+
  ylim(bbox_4326[["ymin"]]+0.0005,bbox_4326[["ymax"]]-0.0003)+
  theme_carto+
  theme(legend.position = "none")

ggsave(here("outcomes","obs_general.jpg"), width = 3000, height = 2000, units = "px", dpi = 200)


bck_atlas +
#ggplot()+
  geom_sf(data = m, lwd = 0.4, col = "red", alpha = 0.1)+
  geom_sf(data = s, alpha = 0.5, col = "red", shape = 3, aes(size = row_total/3))+
  #geom_sf(data = map_tree$osm_points, size = 1, col = "#4A6C6F") +
  geom_sf(data = map_building_civic$osm_polygons, col = "grey80", fill = "grey80") +
  geom_sf(data = st_transform(buildings, 4326), col = "grey80", fill = "grey80")+
  xlim(bbox_4326[["xmin"]]+0.001,bbox_4326[["xmax"]]-0.0005)+
  ylim(bbox_4326[["ymin"]]+0.0007,bbox_4326[["ymax"]]-0.0004)+
  theme_carto+
  theme(legend.position = "none")+
  facet_grid(
    rows = vars(tc),
    cols = vars(date)
  )

ggsave(here("outcomes","obs_general_atlas.jpg"), width = 5000, height = 3000, units = "px", dpi = 200)


bck_atlas +
#ggplot()+
  geom_sf(data = m, lwd = 0.4, col = "red", alpha = 0.1)+
  geom_sf(data = s, alpha = 0.5, col = "red", shape = 3, aes(size = row_total/3))+
  #geom_sf(data = map_tree$osm_points, size = 1, col = "#4A6C6F") +
  geom_sf(data = map_building_civic$osm_polygons, col = "grey80", fill = "grey80") +
  geom_sf(data = st_transform(buildings, 4326), col = "grey80", fill = "grey80")+
  xlim(bbox_4326[["xmin"]]+0.001,bbox_4326[["xmax"]]-0.0005)+
  ylim(bbox_4326[["ymin"]]+0.0007,bbox_4326[["ymax"]]-0.0004)+
  theme_carto+
  theme(legend.position = "none")+
  facet_wrap(~tc,ncol = 4)

ggsave(here("outcomes","obs_general_atlas_heure.jpg"), width = 5000, height = 3000, units = "px", dpi = 200)


bck_atlas +
#ggplot()+
  geom_sf(data = m, lwd = 0.4, col = "red", alpha = 0.1)+
  geom_sf(data = s, alpha = 0.5, col = "red", shape = 3, aes(size = row_total/3))+
  #geom_sf(data = map_tree$osm_points, size = 1, col = "#4A6C6F") +
  geom_sf(data = map_building_civic$osm_polygons, col = "grey80", fill = "grey80") +
  geom_sf(data = st_transform(buildings, 4326), col = "grey80", fill = "grey80")+
  xlim(bbox_4326[["xmin"]]+0.001,bbox_4326[["xmax"]]-0.0005)+
  ylim(bbox_4326[["ymin"]]+0.0007,bbox_4326[["ymax"]]-0.0004)+
  theme_carto+
  theme(legend.position = "none")+
  facet_wrap(~date,ncol = 4)

ggsave(here("outcomes","obs_general_atlas_date.jpg"), width = 5000, height = 3000, units = "px", dpi = 200)

```






## Hexbins by id & fileid

```{r eval=FALSE, include=FALSE}

grid = 
  st_make_grid(
    boundary,
    cellsize = 7,
    square = FALSE) %>% 
  st_sf() %>% 
  st_cast %>%
  mutate(
    id = 1:n())

grid = grid %>%
  mutate(
    int = st_intersects(grid,boundary, sparse = F)
    ) %>%
  filter(int == T) %>%
  dplyr::select(-int)
  
plot(grid)


hexbin_s =
  st_join(
    grid,
    df_s %>% filter(row_total != 0),
    left = FALSE,
    join = st_intersects) %>%
  group_by(id,fileid) %>%
  summarise(
    n = n(),
    date = first(date),
    time = first(tc),
    nbp = sum(row_total),
    gender_male = sum(gender_male),
    gender_female = sum(gender_female))

hexbin_m =
  st_join(
    grid,
    df_m %>% filter(row_total != 0),
    left = FALSE,
    join = st_intersects) %>%
  group_by(id,fileid) %>%
  summarise(
    n = n(),
    date = first(date),
    time = first(tc),
    nbp = sum(row_total),
    gender_male = sum(gender_male),
    gender_female = sum(gender_female))

m_hb = hexbin_m
s_hb = hexbin_s
g_hb = grid

```


```{r eval=FALSE, include=FALSE}

bck +
  geom_sf(data=s_hb, aes(fill = nbp),color = NA)+
  geom_sf(data=g_hb, col = alpha("#757575",0.1),size = 0.01, fill = NA)+
  scale_fill_continuous(type = "viridis",direction = -1)+
  geom_sf(data = map_building_civic$osm_polygons, col = "grey25", fill = "grey25") +
  geom_sf(data = st_transform(buildings, 4326), col = "grey25", fill = "grey25")+
  xlim(bbox_4326[["xmin"]],bbox_4326[["xmax"]])+
  ylim(bbox_4326[["ymin"]],bbox_4326[["ymax"]])+
  theme_carto+
  facet_grid(
    rows = vars(time),
    cols = vars(date)
  ) +
  ggtitle("Situations statiques")
  #theme(legend.position="top")

ggsave(
  here("outcomes","plot_obs_staying_atlas.jpg"),
  width = 6000, height = 4000, units = "px", dpi = 200)


bck +
  geom_sf(data=m_hb, aes(fill = nbp),color = NA)+
  geom_sf(data=g_hb, col = alpha("#757575",0.1),size = 0.01,fill = NA)+
  scale_fill_continuous(type = "viridis",direction = -1)+
  #scale_fill_gradient(low = "#D7E7FE", high = "#02193B")+
  geom_sf(data = map_building_civic$osm_polygons, col = "grey25", fill = "grey25") +
  geom_sf(data = st_transform(buildings, 4326), col = "grey25", fill = "grey25")+
  xlim(bbox_4326[["xmin"]],bbox_4326[["xmax"]])+
  ylim(bbox_4326[["ymin"]],bbox_4326[["ymax"]])+
  ggtitle("Situations en mouvement")+
  theme_carto+
  facet_grid(
    rows = vars(time),
    cols = vars(date)
  )

ggsave(
  here("outcomes","plot_obs_moving_atlas.jpg"),
  width = 6000, height = 4000, units = "px", dpi = 200)

```


#Leaflet
```{r eval=FALSE, include=FALSE}

library(magrittr)
library(leaflet)

leaflet() %>%
  addCircles(data = df_s_4326,
             lng = ~X_wgs84,
             lat = ~Y_wgs84,
             weight = 1,
             radius = ~row_total/3,
             color = "red") %>%
  addPolylines(data = df_m_4326,
               opacity = 0.2,
               weight = 1,
               color = "blue") %>%
  addTiles() %>%
  addProviderTiles(providers$OpenStreetMap.BlackAndWhite) %>%
  addLayersControl(
    overlayGroups = unique(df_s_4326$survey_id),
    options = layersControlOptions(collapsed = FALSE)
  )

```

